---
title: "Introduction to zhuoerdown"
author: "Zhuoer Dong"
date: "`r Sys.Date()`"
output: prettydoc::html_pretty
vignette: >
  %\VignetteIndexEntry{Introduction to zhuoerdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

```{r}
library(zhuoerdown)
```


We use `zhuoerdown` environment varible to distinguish building my own book from building other's book.

Although some part may seem redundant for `zhuoerdown=true`, it make possible to share the same code for both approaches. 



# `.travis.yml`

We offer three examples:

- r4ds: https://github.com/dongzhuoer/build-r4ds/blob/master/.travis.yml
- yihui-blogdown: https://github.com/dongzhuoer/build-yihui-blogdown/blob/master/.travis.yml
- nutshell: https://github.com/dongzhuoer/nutshell/blob/master/.travis.yml



# details

1. Travis add all three tokens to environment variable

# Overview

There are mainly three directories:

- `input/` for input `.Rmd` files
- `output/` for GitBook output
- `repo/` for deploying the output to GitLab

The details of deploying should be moved to nutshell and add a link here.


## parse package dependency

```bash
# possibly used pacakge
cat *.Rmd | grep -Po '[\w\.]+(?=::)' | sort -u | sed 's/$/,/' 
# cited package
cat *.Rmd | grep -Po '(?<=\[@R-)[\w\.]+' | sort -u | sed 's/$/,/' 
```


# customize TOC

- 章超过一页一般就collapse，如 r4ds, rmarkdown
- 所有内容在 2～3页，展开显示，如 blogdown
- 子标题严重不均匀，尤其要展开，如 bookdown



# legacy technical details

The biggest restraint is that `bookdown::render_book()` requires workspace at the book folder.

For _blogdown_, `.Rmd` lives in `docs/`. If you `setwd()` to there, many paths would be relative to it (like `../../output`, `../../extra/_output.yaml`). 

So I thought about adding a environment variable `input_sub_dir`. But _blogdown_ doesn't collaborate, it refer to the some source code of the package by `../R/***.R`.

Suddenly, I realized that instead of setting every path relative to workspace, we can have `to_work_dir` to walk to `$work_dir`. In this way, every other path remains unchanged (`output`, `extra/_output.yaml`), user only need to customize `rmd_dir` & `to_work_dir`, like `rmd_dir=.; to_work_dir=..;`, `rmd_dir=docs; to_work_dir=../..;`.


